One Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985

### 2023-02-16 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
legend of figures

```{r Figure mixed, fig.cap="Mixed-types problem-constructions in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
#summary(as.factor(ama_mx$mx_cat))
ama_mx %>%
  count(mx_cat, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>%
  filter(mx_cat == "Mixed-types") %>%
  ggplot() +
  geom_smooth(aes(x=as.numeric(year), y = perc, color = mx_cat),
          	se = FALSE, linewidth =0.75, linetype="solid") +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits=c(0,.4)) +
  labs(x = "", y = "", title ="Share of mixed-types problem-constructions by year",
   	subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
   	caption = "Curves in the plot were smoothed using loess method.") +
  theme_am() +
  scale_color_manual(values = "yellow3")
```

@@

The authors are extremely grateful to Graziella Moraes Silva, James Hollway, and Matias López for their support. The authors would also like the two anonymous reviewers for their comments and suggestions. Finally, we would like to thank Anna, Federico, Mario, and Rodrigo for their invaluable help.

>>>>

```{r Figure mixed, fig.cap="Mixed-types problem-constructions in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
#summary(as.factor(ama_mx$mx_cat))
ama_mx %>%
  count(mx_cat, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>%
  filter(mx_cat == "Mixed-types") %>%
  ggplot() +
  geom_smooth(aes(x=as.numeric(year), y = perc, color = mx_cat),
          	se = FALSE, linewidth =0.75, linetype="solid") +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Share of mixed-types problem-constructions by year",
   	subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
   	caption = "Curves in the plot were smoothed using loess method.") +
  theme_am() +
  scale_color_manual(values = "yellow3")

@@

The authors are extremely grateful to Graziella Moraes Silva, James Hollway, and Matias López for their support. The authors would also like to thank the anonymous reviewers, Anna, Federico, Mario, and Rodrigo for their invaluable help.
